---
title: "cia3"
author: "Anshu Singh"
date: "2023-04-28"
output:
  word_document: default
  html_document: default
  pdf_document: default
runtime: shiny
---



```{r}
install.packages("knitr")
```

```{r}
install.packages("contrib.url")

```
```{r}
install.packages("dplyr")
```
```{r}
install.packages("tidyverse")
```
```{r}
library(tidyverse)
```


```{r}
# loading the the Data
setwd("C:/Users/Admin/OneDrive/Desktop/R")
Data=read.csv("Data.csv")
Data
```

```{r}

library(dplyr)
# Example 1 
sample_n(Data,3)

```

Uni variate Analysis of Variable

```{r}
distinct(Data)
```

```{r}
is.na(Data)
```
```{r}
duplicated(Data)
```
```{r}
summary(Data)
```
```{r}
install.packages("ggplot2")
```
```{r}
library(ggplot2)
```

```{r}
boxplot(Data$chanise.demand,col="#e8f48c")
boxplot(Data$price,col="#e8f48c")
boxplot(Data$TEU.USA,col="#e8f48c")
boxplot(Data$demand,col="#e8f48c")
boxplot(Data$GPRD,col="#e8f48c")
boxplot(Data$GPRDACT,col="#e8f48c")
boxplot(Data$GPRDTHREAT,col="#e8f48c")
boxplot(Data$supply,col="#e8f48c")
boxplot(Data$environment.regulation,col="#e8f48c")
boxplot(Data$exchage.rate,col="#e8f48c")
boxplot(Data$INFLATION.RATE,col="#e8f48c")
boxplot(Data$minig.out.put,col="#e8f48c")
boxplot(Data$spx,col="#e8f48c")
```


```{r}
df <- data.frame (group = rep(c("chanise.demand","price","X","TEU.USA","X.1","GPRD", "GPRD_ACT","GPRD_THREAT","X.2","X.3","X.4","X.5","X.6","spx"), each = 50), 
value = c(rnorm (50, mean =5,sd=1),
rnorm (50, mean =8,sd=2)))

ggplot(df, aes (x = group, y = value)) + geom_boxplot (color= "black",fill = "brown") + labs(title = "Box Plot")
```



```{r}
#for chanise.demand
outliers <- boxplot(Data$chanise.demand, plot = FALSE)$out
data_clean <- Data$chanise.demand[!Data$chanise.demand %in% outliers]
boxplot(data_clean,col="#7fff00")
#for Price
outliers1 <- boxplot(Data$price, plot = FALSE)$out
data_clean1 <- Data$price[!Data$price %in% outliers1]
boxplot(data_clean1,col="#7fff00")
#for TEU.USA
outliers2 <- boxplot(Data$TEU.USA, plot = FALSE)$out
data_clean2 <- Data$TEU.USA[!Data$TEU.USA %in% outliers2]
boxplot(data_clean2,col="#7fff00")
#for demand
outliers3 <- boxplot(Data$demand, plot = FALSE)$out
data_clean3 <- Data$demand[!Data$demand %in% outliers3]
boxplot(data_clean3,col="#7fff00")
#for GPRD_ACT
outliers4 <- boxplot(Data$GPRDACT, plot = FALSE)$out
data_clean4 <- Data$GPRDACT[!Data$GPRDACT %in% outliers4]
boxplot(data_clean4,col="#7fff00")
#for GPRD_THREAT
outliers5 <- boxplot(Data$GPRDTHREAT, plot = FALSE)$out
data_clean5 <- Data$GPRDTHREAT[!Data$GPRDTHREAT %in% outliers5]
boxplot(data_clean5,col="#7fff00")
#for supply
outliers6 <- boxplot(Data$supply, plot = FALSE)$out
data_clean6 <- Data$supply[!Data$supply %in% outliers6]
boxplot(data_clean6,col="#7fff00")
#for environment.regulation
outliers7 <- boxplot(Data$environment.regulation, plot = FALSE)$out
data_clean7 <- Data$environment.regulation[!Data$environment.regulation %in% outliers7]
boxplot(data_clean7,col="#7fff00")
#for exchage.rate
outliers8 <- boxplot(Data$exchage.rate, plot = FALSE)$out
data_clean8 <- Data$exchage.rate[!Data$exchage.rate %in% outliers8]
boxplot(data_clean8,col="#7fff00")
#for INFLATION.RATE
outliers9 <- boxplot(Data$INFLATION.RATE, plot = FALSE)$out
data_clean9 <- Data$INFLATION.RATE[!Data$INFLATION.RATE %in% outliers9]
boxplot(data_clean9,col="#7fff00")
#for minig.out.put
outliers10 <- boxplot(Data$minig.out.put, plot = FALSE)$out
data_clean10 <- Data$minig.out.put[!Data$minig.out.put %in% outliers10]
boxplot(data_clean10,col="#7fff00")
#for spx
outliers11 <- boxplot(Data$spx, plot = FALSE)$out
data_clean11 <- Data$spx[!Data$spx %in% outliers11]
boxplot(data_clean11,col="#7fff00")


```
 Bivariate Analysis of variable
```{r}
#a=data.frame(x=c(data_clean),y=c(data_clean1)
#ggplot(a,aes(x,y)) + geom_point(color = "Red", size= 5) + labs(title = "ScatterPlot" )
plot(Data$price, Data$TEU.USA, col = "#ef3038", xlab = "Price", ylab = "TEU USA", main = "price~TEU.USA")

plot(Data$price, Data$chanise.demand, col = "#dda0dd", xlab = "Price", ylab = "TEU USA", main = "price~chanise.demand")

plot(Data$price, Data$demand, col = "#7b68ee", xlab = "Price", ylab = "TEU USA", main = "price~demand")
plot(Data$price, Data$GPRD, col = "#ef3038", xlab = "Price", ylab = "TEU USA", main = "price~GPRD")

plot(Data$price, Data$GPRDACT, col = "#7b68ee", xlab = "Price", ylab = "TEU USA", main = "price~GPRDACT")
plot(Data$price, Data$GPRDTHREAT, col = "#dda0dd", xlab = "Price", ylab = "TEU USA", main = "price~GPRDTHREAT")
plot(Data$price, Data$supply, col = "#ef3038", xlab = "Price", ylab = "TEU USA", main = "price~supply")
plot(Data$price, Data$environment.regulation, col = "#7b68ee", xlab = "Price", ylab = "TEU USA", main = "price~environment.regulation")
plot(Data$price, Data$exchage.rate, col = "#ef3038", xlab = "Price", ylab = "TEU USA", main = "price~exchage.rate")
plot(Data$price, Data$INFLATION.RATE, col = "#dda0dd", xlab = "Price", ylab = "TEU USA", main = "price~INFLATION.RATE")
plot(Data$price, Data$minig.out.put, col = "#7b68ee", xlab = "Price", ylab = "TEU USA", main = "price~minig.out.put")
plot(Data$price, Data$spx, col = "#ef3038", xlab = "Price", ylab = "TEU USA", main = "price~spx")

```


7. Cross Tab Analysis of relevant Variable

```{r}
mydata=data.frame(Data$GPRD,Data$GPRDACT)
# Create a contingency table using xtabs()
mytable=xtabs(~GPRD+GPRDACT,data=Data)
# Print the contingency table
print(mytable)
barplot(mytable,col="#5865F2")

```
8. Statistical Analysis of Continuous Variable


```{r}

#TEU.USA
summary(Data$TEU.USA)
#supply
summary(Data$supply)
#demand
summary(Data$demand)
#environment.regulation
summary(Data$environment.regulation)
#chanise.demand
summary(Data$chanise.demand)
#exchage.rate
summary(Data$exchage.rate)
#INFLATION.RATE
summary(Data$INFLATION.RATE)
#minig.out.put
summary(Data$minig.out.put)
#Spx
summary(Data$spx)
#price
summary(Data$price)
```
```{r}
x = Data$chanise.demand
mode_x = names(sort(table(x), decreasing = TRUE)[1])

# Print the mode
print(mode_x)

x1 = Data$price
mode_x1 = names(sort(table(x1), decreasing = TRUE)[1])

# Print the mode
print(mode_x1)
x2 = Data$demand
mode_x2 = names(sort(table(x2), decreasing = TRUE)[1])

# Print the mode
print(mode_x2)
x3 = Data$supply
mode_x3 = names(sort(table(x3), decreasing = TRUE)[1])

# Print the mode
print(mode_x3)
x4 = Data$environment.regulation
mode_x4 = names(sort(table(x4), decreasing = TRUE)[1])

# Print the mode
print(mode_x4)
x5 = Data$TEU.USA
mode_x5 = names(sort(table(x5), decreasing = TRUE)[1])

# Print the mode
print(mode_x5)
x6 = Data$exchage.rate
mode_x6 = names(sort(table(x6), decreasing = TRUE)[1])

# Print the mode
print(mode_x6)
x7 = Data$INFLATION.RATE
mode_x7 = names(sort(table(x7), decreasing = TRUE)[1])

# Print the mode
print(mode_x7)
x8 = Data$spx
mode_x8 = names(sort(table(x8), decreasing = TRUE)[1])

# Print the mode
print(mode_x8)
x9 = Data$minig.out.put
mode_x9 = names(sort(table(x9), decreasing = TRUE)[1])

# Print the mode
print(mode_x9)
```

```{r}
sd <- sd(Data$price)
var <- var(Data$price)
cat("Standard deviation: price=", sd, "\n")
cat("Variance:price=", var, "\n")

sd1 <- sd(Data$demand)
var1 <- var(Data$demand)
cat("Standard deviation:demand=", sd1, "\n")
cat("Variance:demand=", var1, "\n")

sd2 <- sd(Data$TEU.USA)
var2 <- var(Data$TEU.USA)
cat("Standard deviation: TEU.USA)e=", sd2, "\n")
cat("Variance:TEU.USA)=", var2, "\n")


sd3 <- sd(Data$supply)
var3 <- var(Data$supply)
cat("Standard deviation: supply=", sd3, "\n")
cat("Variance:supply=", var3, "\n")

sd4 <- sd(Data$environment.regulation)
var4 <- var(Data$environment.regulation)
cat("Standard deviation: environment.regulation=", sd4, "\n")
cat("Variance:environment.regulation=", var4, "\n")

sd5 <- sd(Data$INFLATION.RATE)
var5 <- var(Data$INFLATION.RATE)
cat("Standard deviation: INFLATION.RATE=", sd5, "\n")
cat("Variance:INFLATION.RATE=", var5, "\n")

sd6 <- sd(Data$exchage.rate)
var6 <- var(Data$exchage.rate)
cat("Standard deviation: exchage.rate=", sd6, "\n")
cat("Variance:exchage.rate =", var6, "\n")

sd7 <- sd(Data$spx)
var7 <- var(Data$spx)
cat("Standard deviation:spx =", sd7, "\n")
cat("Variance:spx =", var7, "\n")

sd8 <- sd(Data$minig.out.put)
var8 <- var(Data$minig.out.put)
cat("Standard deviation:minig.out.put =", sd8, "\n")
cat("Variance:minig.out.put =", var8, "\n")

```

9. Underlying Hypothesis

Annova
```{r}
model <- aov(price ~ chanise.demand, data = Data)

# Print the ANOVA table
summary(model)


model1 <- aov(price ~ demand, data = Data)

# Print the ANOVA table
summary(model1)

model2 <- aov(price ~ TEU.USA, data = Data)

# Print the ANOVA table
summary(model2)
model3 <- aov(price ~ supply, data = Data)

# Print the ANOVA table
summary(model3)
model4 <- aov(price ~ environment.regulation, data = Data)

# Print the ANOVA table
summary(model4)
model5 <- aov(price ~ exchage.rate, data = Data)

# Print the ANOVA table
summary(model5)
model6 <- aov(price ~ INFLATION.RATE, data = Data)

# Print the ANOVA table
summary(model6)

model7 <- aov(price ~ minig.out.put, data = Data)

# Print the ANOVA table
summary(model7)
model8 <- aov(price ~ spx, data = Data)

# Print the ANOVA table
summary(model8)
model9 <- aov(price ~ GPRD, data = Data)

# Print the ANOVA table
summary(model9)
model10 <- aov(price ~ GPRDACT, data = Data)

# Print the ANOVA table
summary(model10)

model11 <- aov(price ~ GPRDTHREAT, data = Data)

# Print the ANOVA table
summary(model11)

```
 Regration
 
```{r}
fit=lm(demand ~ price , data=Data)
#view summary of model
summary(fit)
fit1=lm(chanise.demand ~ price , data=Data)
#view summary of model
summary(fit1)

fit2=lm(TEU.USA ~ price , data=Data)
#view summary of model
summary(fit2)
fit3=lm(supply ~ price , data=Data)
#view summary of model
summary(fit3)

fit8=lm(GPRD ~ price , data=Data)
#view summary of model
summary(fit8)
fit5=lm(GPRDACT ~ price , data=Data)
#view summary of model
summary(fit5)
fit6=lm(GPRDTHREAT ~ price , data=Data)
#view summary of model
summary(fit6)
fit7=lm(environment.regulation~ price , data=Data)
#view summary of model
summary(fit7)
fit4=lm(exchage.rate ~ price , data=Data)
#view summary of model
summary(fit4)
fit9=lm(minig.out.put ~ price , data=Data)
#view summary of model
summary(fit9)
fit10=lm(INFLATION.RATE ~ price , data=Data)
#view summary of model
summary(fit10)
fit11=lm(spx ~ price , data=Data)
#view summary of model
summary(fit11)

```
t-test
```{r}
t.test(Data$price,Data$demand, var.equal=FALSE)
t.test(Data$price,Data$chanise.demand, var.equal=FALSE)
t.test(Data$price,Data$supply, var.equal=FALSE)
t.test(Data$price,Data$TEU.USA, var.equal=FALSE)
t.test(Data$price,Data$environment.regulation, var.equal=FALSE)
t.test(Data$price,Data$INFLATION.RATE, var.equal=FALSE)
t.test(Data$price,Data$exchage.rate, var.equal=FALSE)
t.test(Data$price,Data$GPRD, var.equal=FALSE)
t.test(Data$price,Data$GPRDACT, var.equal=FALSE)
t.test(Data$price,Data$GPRDTHREAT, var.equal=FALSE)
t.test(Data$price,Data$minig.out.put, var.equal=FALSE)
t.test(Data$price,Data$spx, var.equal=FALSE)
```

10. Multicollinearity Analysis

```{r}
install.packages("olsrr")

```
```{r}
library("olsrr")
```


```{r}
# Fit a linear regression model for mpg on cyl, disp, and hp
m=lm(price ~ demand + chanise.demand + supply + TEU.USA + GPRDACT  , data = Data)

# Calculate VIF for each predictor
olsviftol<- round(1 / (1 - summary(m)$r.squared), 2)

# Compute the variance inflation factors (VIF)
olsviftol
```
```{r}
# Residual analysis
plot(model1, which = 1) # Residuals vs Fitted
plot(model3, which = 2) # Normal Q-Q plot
plot(model5, which = 3) # Scale-Location plot
plot(model10, which = 4) # Residuals vs Leverage
```


11. Correlations Analysis
```{r}
install.packages("corrplot")
```

```{r}
library(corrplot)

# Compute the correlation matrix
corr_matrix <- cor(Data[c("price","demand","GPRD","GPRDACT","GPRDTHREAT","environment.regulation","minig.out.put" )])

# Create the correlation plot
corrplot(corr_matrix, method = "circle", type = "upper", tl.col = "black")

```

12.Feature Selection
```{r}
base.mod =lm(price ~ demand + chanise.demand + supply + TEU.USA + GPRD + GPRDACT + GPRDTHREAT + environment.regulation + exchage.rate + INFLATION.RATE + minig.out.put + spx , data = Data)

# base intercept only model
all.mod=lm(price ~ demand + chanise.demand + supply + TEU.USA + GPRD + GPRDACT + GPRDTHREAT + environment.regulation + exchage.rate + INFLATION.RATE + minig.out.put + spx , data = Data) # full model with all predictors

stepMod <- step(base.mod, scope = list(lower = base.mod, upper = all.mod), direction = "both", trace = 0, steps = 1000)  # perform step-wise algorithm

shortlistedVars <- names(unlist(stepMod[[1]])) # get the shortlisted variable.

shortlistedVars <- shortlistedVars[!shortlistedVars %in% "(Intercept)"]  # remove intercept 
print(shortlistedVars)
```


13. Modelling Method Applied (Linear Regression) using different data transformation technique
```{r}
install.packages("ggpubr")
```
```{r}
library(ggpubr)
```

```{r}
install.packages("MASS")
```

```{r}
library(MASS)
```
```{r}
cor(Data$demand,Data$price)
cor(Data$supply,Data$price)
cor(Data$TEU.USA,Data$price)
cor(Data$GPRD,Data$price)
```

```{r}

# Create the QQ plot
qqnorm("demand","price", Data)
title("QQ Plot")
xlab("demand")
ylab("price")


```



```{r}
m1 <- lm(price ~ demand +  supply + exchage.rate + GPRDTHREAT, data = Data)
summary(m1)

# Get the coefficients for the model
coef(m1)
boxcox(m1, lambda = seq(-2,2,0.1),)
```
```{r}
library(dplyr)

ols_to_log<-c("demand","supply","TEU.USA","minig.out.put")

# Apply the logarithm to the selected columns
log_data <- Data%>%
  mutate(across(all_of(cols_to_log),log))
# Print the results
print(log_data)
```



14. Residual Analysis
```{r}
residuals <- resid(m1)

# Plot the residuals against the fitted values
plot(fitted(m1), residuals, 
     xlab = "Fitted Values", ylab = "Residuals",
     main = "Residual Plot" , col="#E9AB17")

# Add a horizontal line at y = 0 for reference
abline(h=0)
```

15. Model Diagnostics

```{r}
install.packages("shiny")

```

```{r}
library(shiny)
library(ggplot2)

# Define UI
ui <- fluidPage(
  titlePanel("Predicted Copper Price Calculator"),
  sidebarLayout(
    sidebarPanel(
      numericInput("ad_spend", "Advertising Spend:", value = 50),
      numericInput("num_stores", "Number of Stores:", value = 100),
      numericInput("avg_price", "Average Price of Products:", value=200),
      numericInput("store_size", "Store Size:", value = 500),
      numericInput("cust_satisfaction", "Customer Satisfaction:", value = 75),
      numericInput("sales_promotions", "Sales Promotions:", value = 150),
      numericInput("ecommerce_presence", "E-commerce Presence:", value = 300),
      numericInput("num_competitors", "Number of Competitors:", value = 600),
      numericInput("seasonality", "Seasonality:", value = 90),
      numericInput("economic_indicators", "Economic Indicators:", value = 180),
      numericInput("product_variety", "Product Variety:", value =360),
      numericInput("brand_reputation", "Brand Reputation:", value =720),
      actionButton("calculate", "Calculate Predicted Copper Price")
    ),
    mainPanel(
      plotOutput("diagnostic_plot")
    )
  )
)

# Define server
server <- function(input, output) {
  
  # Reactive expression for predicted copper price
  predicted_price <- reactive({
    req(input$calculate)
    
    # Model based on input variables
    copper_price <- input$ad_spend * 0.1 + input$num_stores * 0.5 + input$avg_price * 0.2 +
      input$store_size * 0.3 + input$cust_satisfaction * 0.15 + input$sales_promotions * 0.2 +
      input$ecommerce_presence * 0.1 + input$num_competitors * 0.05 + input$seasonality * 0.3 +
      input$economic_indicators * 0.2 + input$product_variety * 0.15 + input$brand_reputation * 0.1
    
    copper_price
  })
  
  # Render diagnostic plot
  output$diagnostic_plot <- renderPlot({
    # Plot predicted copper price vs. input variables
    ggplot(data.frame(x = predicted_price(), y = c(input$ad_spend, input$num_stores, input$avg_price,
                                                   input$store_size, input$cust_satisfaction, input$sales_promotions,
                                                   input$ecommerce_presence, input$num_competitors, input$seasonality,
                                                   input$economic_indicators, input$product_variety, input$brand_reputation)), 
           aes(x = x, y = y)) +
      geom_point() +
      labs(x = "Predicted Copper Price", y = "Input Variables")
  })
}

# Run the app
shinyApp(ui, server)

```

